On Sample Size for Block Bootstrap Confidence Intervals to Have Desired Coverage Rates

### 2023-05-10 Manuscript/manuscript.tex
5/10 Manuscript Update

The goal of this paper is to provide some practical recommendations on
necessary sample size for block bootstrap with dependent data. We consider a
simple situation of a stationary time series, where the parameters of
interests are the mean, standard deviation, and the first-order
autocorrelation coefficient. We compare three variants of block bootstrap
CIs from the literature \citep{diciccio1996bootstrap,
  rice2006mathematical}: a basic percentile interval, a percentile
interval centered around the estimate, and a bias-corrected and
accelerated ($BC_a$) interval also centered around the original estimate. Their
empirical coverage rates at different sample sizes and dependence levels are
compared in a simulation study. The results of this study suggest that
appropriate recovery of temporal dependence parameters is heavily dependent on
the type of interval used.

@@

Alternatively, block-bootstrap can be done with overlapping or moving blocks.
Define moving blocks $Z_j = \{X_j, \ldots, X_{j + l - 1}\}$,
$j = 1, \ldots, n - l + 1$. Now we draw $k$ blocks from the $(n - l + 1)$
blocks
of $Z_j$'s with replacement and then align them in the order they were
picked
to form a block bootstrap sample. If $n$ is not a multiple of~$l$, the last
block selected will be reduced in size so that the final size of the
block bootstrap sample is $n$. It is also possible to implement moving block
bootstrap while allowing blocks to wrap around the end of the series. In other
words, define moving blocks (assuming $l > 1$) as:
\jy{Any equation must be a part of a sentence and should be punctuated.}
\jy{Recall a blank line means a new paragraph.}
\jy{Define your response command with color and respond}
\mc{addressed above comments}
\begin{equation}
Z_j =
    \begin{cases}
        \{X_j, \ldots, X_{j + l - 1}\} & \text{if } j = 1, \dots, n - l + 1\\
        \{X_j, \ldots, X_n, X_1, \ldots, X_{j-n+l-1}\} & \text{if } j = n - l
        + 2 ,\dots, n.
    \end{cases}
\end{equation}
\jy{The ending index does not seem right}
\mc{addressed above}
The second version of moving block bootstrap was used in
this study because it is the implementation provided in the function
\texttt{tsboot} from R package \textsl{boot} \citep{boot}, and it is easier
overall because $l$ need not divide $n$.
\jy{state we use it because it is implemented in package boot and cite boot}  
\jy{This reference is from a low-tier journal. Find something from a stronger
  journal?}
\mc{addressed above comments}
The block size~$l$ needs to chosen with care. It needs to be large enough for
each bootstrap sample to preserve the serial dependence, yet small enough for
there to be some variability between each bootstrap sample. As $n$ increases,
$l$ should also increase, but $l / n$ should decrease. To achieve this, $l$ is
often assigned a value as a function of $n$. A common function that is
considered the best by much previous literature is $l = \lceil n^{1/3} \rceil$
\citep{buhlmann1999block}.

@@

Suppose that we have repeated the steps in the last subsection $B$ times, and
that for $b \in \{1, \ldots, B\}$, we have obtained an estimator
$\hat\theta_n^{(b)}$ based on the $b$th bootstrap sample using the same method
that was applied to $\{X_t: t = 1, \ldots, n\}$ to obtain $\hat\theta_n$.
Now the question is, how to construct a CI for $\theta$
using the $B$ bootstrap point estimates
$\{\hat\theta_n^{(1)}, \ldots, \hat\theta_n^{(B)}\}$.
We consider three kinds of CIs.

\jy{can we give references to each of the method? How about the review paper in
  Statistical Science?}

@@

\paragraph{Bias Corrected and Accelerated ($BC_a$) Bootstrap CI}
The $BC_a$ CI was first suggested in \citet{efron1987better}.
\eds{a different abbrevation/notation was used for this in the introduction}
\mc{used $BC_a$}
\jy{Isn't this just the empirical CDF? We just need the sample quantile functon.
  What is your reference for this description?}
Let $\hat{z}_0 = \Phi^{-1}\{\#\{\hat\theta_n^{(b)} < \hat{\theta}_n\} / B\}$ for $b \in \{1, \ldots, B\}$. 
Let $Z_{(i)}$ be the original sample without the $i$th block $z_i$, and let
$\hat{\theta}_{n, -i}$ be the jackknife values of $Z_{(i)}$ for $i \in \{1, \ldots, n\}$, 
and let $a$ be $SKEW\{\hat{\theta}_{n, -i}\} / 6$. Then
 $\hat\theta_{BC_a}[\alpha] = \hat{G}^{-1}\Phi(z_0 + \frac{z_{0} + z_{\alpha}}{1 - a(z_{0} + z_{\alpha})}).$ \eds{notation will need to be cleaned and clarified}
A $(1 - \alpha)$ centered $BC_a$ CI is
\[
(\hat\theta_{BC_a}[\alpha/2], \quad
\hat\theta_{BC_a}[1 - \alpha/2]).
\]
This CI is not necessarily centered by the point estimator $\hat\theta_n$. The
$BC_a$ method corrects for bias and skewness of the $B$ bootstrap point
estimates $\{\hat\theta_n^{(1)}, \ldots, \hat\theta_n^{(B)}\}$ by including
bias-correction and acceleration factors. 
\jy{why is it called BCA?}
\mc{addressed}

\paragraph{Standard Normal CI}
A $(1 - \alpha$ standard normal CI is
\[
(\hat{\theta}_{n} - z_{(1-\alpha/2)}*\hat{se}, \hat{\theta}_{n} - z_{(\alpha/2)}*\hat{se}.
\]
This CI is centered by the point estimator $\hat\theta_n$ and is symmetric.

\paragraph{Student's t CI}
A $(1 - \alpha$ student's t CI is
\[
(\hat{\theta}_{n} - t_{(1-\alpha/2), k - 1}*\hat{se}, \hat{\theta}_{n} - t_{(\alpha/2), k -1}*\hat{se}.
\]
This CI is centered by the point estimator $\hat\theta_n$ and is symmetric.

@@

Three target parameters of $X_t$ were considered:
1) $\mu = 0$, the mean of $X_t$;
2) $\sigma_x^2 = 1$, the variance of $X_t$; and
2) $\phi$, the lag-1 auto-correlation coefficient.
To investigate the effect of sample size~$n$, we considered an array of values
$n \in \{100, 200, \ldots, 1000\}$. In each configuration, we generated 10000
replicates. For each replicate, we constructed three 95\% block bootstrap
CIs for each parameter as described in the last section, and
estimated their actual coverage rates along with their 95\% confidence
intervals from the 10000 replicates. The block bootstrap sampling step was done
with function \texttt{tsboot} from R package \textsl{boot} \citep{boot}, with
block size $\lceil n / l \rceil$. This function by default is an implementation
of moving block bootstrap as described in the previous section.
\jy{size? also it was overlapping blocks. Describe the details here.}
\eds{Is $l = \lceil n^{1/3} \rceil$? Is it also worth investigating different 
choices of $l$ for fixed (large) $n$?}
\eds{how did you estimate $\mu$, $\sigma_x$ and $\phi$?}

@@

\jy{Make it flow better and conciser}
The coverage rates of the CIs were used to compare the performance of CIs. Let
$\hat\theta_{L, r}$ and $\hat\theta_{U, r}$ be the lower and upper bound,
respectively, for the confidence interval constructed for each replicate
$r \in \{1, \ldots, R\}$, where $R$ is the
number of replicates.
Then $cov = \#\{\hat\theta_{L, r} < \theta < \hat\theta_{U, r} \}/R$,  
for $r \in \{1, \ldots, R\}$.
\eds{this notation is a bit sloppy, as it implies $n_{CI}$ changes for each 
value of $CI$; consider using a summation of indicators with a different index}
\mc{replaced $CI$ with $r$, and $n_{CI}$ with $R$}
The coverage rate is, of course, a
point estimate of a proportion, so a 95\% CI of this coverage
proportion (with $n_{CI} = 10000$) can be constructed. If the proportion
0.95 is included in the interval, the block bootstrap method is likely
performing
well. If all values in the interval are below 0.95, the results would suggest 
that the
method either is providing inaccurate estimation, is underestimating the
process' variability, or a combination of both. If all values in the interval
are above .95, the results suggest that the method is overestimating the
process' variability.

If $\theta$ is not covered at that $n$, a larger $n$ may be
necessary, assuming that performance will improve as $n$ is increased. $n =$
\jy{learn from how I presented this}
100, 200, 400, 800, and 1600 were used in this study. Remember that
the goal of this study is to find the smallest $n$ which is sufficient for
proper coverage.

@@

\jy{One paragraph for each parameter; write down your observations in bullet
  points and then organize them into a logically flowing paragraph.}

% mu
%As dependence gets stronger, a larger sample size is necessary. 
%For $\mu$, Percentile, Centered, and BCA, and Standard more or less 
% need about the same 
% For phi = -0.4, they slightly over-cover mu for all sample sizes, but 
% the error bars generally hover around the 95% line
% For phi = -0.2, all four cover mu at the nominal rate when n = 400, and when 
% n = 1600, although there is a dip in coverage for n = 800.
% Besides that, the coverage rates remain about .9375 for all sample sizes
% For phi = 0, n = 1600 seems to be enough
% For phi = 0.2, the coverage rates are above .9375 when n = 800 and 1600.
% Although there is a slight downward trend from 800 to 1600
% For phi = 0.4, the coverage rates are above .925 when n = 800 and 1600.
% Although there is a more noticeable downward trend from 800 to 1600.
% Student's t performs noticeably better
% For phi = -0.4, it over-covers mu for all sample sizes, and the lower bounds
% are all above the line
%For phi = -0.2, it slightly over-covers mu, and the error bars generally hover
% around the line
% For phi = 0, the interval for mu's coverage rate contains .95 for all sample sizes
% For phi = 0.2 and 0.4, the trend in coverage is similar to the other intervals, but 
% the overall coverage rates are higher.
% The deviations in trend
% for all intervals can be most likely be attributed to noise.

% sigma
%As dependence gets stronger, a larger sample size is necessary. 
% BCA greatly undercovers for all sample sizes, but no trend of coverage deterioration
% Should not be used
%For $\sigma$, Percentile, Centered, and Standard Ci perform similarly
% For phi = -0.4, -0.2, and 0, n = 1600 seems nearly enough to cover sigma at the 
% nomal rate
% For phi = 0.2 and 0.4, a larger sample size seems to be necessary to cover at nominal rate, 
% 0.2: n = 800 and 1600, coverage is above .93 for all three intervals
% 0.4: But at n = 1600, coverage is above .93 for all three intervals
% Student's t performs well
% For phi = -0.4, sigma is covered at the nominal rate for n >= 1600
% For phi = -0.2, sigma is covered at the nominal rate for n >= 400
% For phi = 0, sigma is covered at the nominal rate for n >= 400
% For phi = 0.2, coverage seems to level out at n = 400, but seems to be around .945
% For phi = 0.4, coverage does not seem to increase much from n = 400 onwards, but is above .93
% The deviations in trend
% for all intervlas can be most likely be attributed to noise.

%phi
%As dependence gets stronger, a larger sample size is necessary. 
%Percentile and BCA deteriorate clearly for any level of temporal correlation 
%Regardless of negative or positive
%Should not be used
%Centered and Standard perform similarly
%For these a sample size of n = 800 appears to be necessary to recover phi at the nominal level
% Student's t appears to recover phi at the nominal level for n >= 100
\jy{One summary paragraph at the end.}

To summarize, the CI type chosen should be based on the target parameter.
...

@@

When using $\hat{\theta}_{n}$-centered intervals and $\phi$ is
unknown, the results of this study suggest that an $n$ of around 500 may be
necessary for common practice to estimate a simple parameter like $\mu$, and
an $n$ of around 400 may be necessary to
estimate $\sigma_x$. If $\phi$ is already known, a lesser $n$ may be adequate to
estimate these parameters. When $\phi$ was negative, a $n$ of around 100 was
sufficient to estimate $\mu$. However, in real world applications, $\phi$ is
more commonly found to be positive, so a larger $n$ is more likely to be
necessary. Lastly, to estimate $\phi$, an $n$ of around 400 may be necessary.
Further investigation may be necessary to see if there are other interval
corrections that fix the coverage deterioration problem for $\phi$.

>>>>

The goal of this paper is to provide some practical recommendations on
necessary sample size for block bootstrap with dependent data. We consider a
simple situation of a stationary time series, where the parameters of
interests are the mean, standard deviation, and the first-order
autocorrelation coefficient. We compare five variants of block bootstrap
CIs from the literature \citep{diciccio1996bootstrap,
  rice2006mathematical}: a basic percentile interval, a percentile
interval centered around the estimate, a bias-corrected and
accelerated ($BC_a$) interval, a standard normal interval, and a student's $t$
interval. Their
empirical coverage rates at different sample sizes and dependence levels are
compared in a simulation study. The results of this study suggest that
appropriate recovery of temporal dependence parameters is heavily dependent on
the type of interval used.

@@

Alternatively, block-bootstrap can be done with overlapping or moving blocks.
Define moving blocks $Z_j = \{X_j, \ldots, X_{j + l - 1}\}$,
$j = 1, \ldots, n - l + 1$. Now we draw $k$ blocks from the $(n - l + 1)$
blocks
of $Z_j$'s with replacement and then align them in the order they were
picked
to form a block bootstrap sample. If $n$ is not a multiple of~$l$, the last
block selected will be reduced in size so that the final size of the
block bootstrap sample is $n$. It is also possible to implement moving block
bootstrap while allowing blocks to wrap around the end of the series. In other
words, define moving blocks (assuming $l > 1$) as:
\jy{Any equation must be a part of a sentence and should be punctuated.}
\jy{Recall a blank line means a new paragraph.}
\jy{Define your response command with color and respond}
\mc{addressed above comments}
\begin{equation}
Z_j =
    \begin{cases}
        \{X_j, \ldots, X_{j + l - 1}\} & \text{if } j = 1, \dots, n - l + 1\\
        \{X_j, \ldots, X_n, X_1, \ldots, X_{j-n+l-1}\} & \text{if } j = n - l
        + 2 ,\dots, n.
    \end{cases}
\end{equation}
\jy{The ending index does not seem right}
\mc{addressed above}
The second version of moving block bootstrap was used in
this study because it is the implementation provided in the function
\texttt{tsboot} from R package \textsl{boot} \citep{boot}, and it is easier
overall because $l$ need not divide $n$.
\jy{state we use it because it is implemented in package boot and cite boot}  
\jy{This reference is from a low-tier journal. Find something from a stronger
  journal?}
\mc{addressed above comments}
The block size~$l$ needs to chosen with care. It needs to be large enough for
each bootstrap sample to preserve the serial dependence, yet small enough for
there to be some variability between each bootstrap sample. As $n$ increases,
$l$ should also increase, but $l / n$ should decrease. To achieve this, $l$ is
often assigned a value as a function of $n$. A common function that is
considered the best by much previous literature is $l = \lceil n^{1/3} \rceil$
\citep{buhlmann1999block}, which is how the value of $l$ was determined for
this
study. It may be worth investigating in a future study if another block size
scheme is 
optimal for the context of a time series by comparing different block sizes
whilst keeping the sample size fixed.

@@

Suppose that we have repeated the steps in the last subsection $B$ times, and
that for $b \in \{1, \ldots, B\}$, we have obtained an estimator
$\hat\theta_n^{(b)}$ based on the $b$th bootstrap sample using the same method
that was applied to $\{X_t: t = 1, \ldots, n\}$ to obtain $\hat\theta_n$.
Now the question is, how to construct a CI for $\theta$
using the $B$ bootstrap point estimates
$\{\hat\theta_n^{(1)}, \ldots, \hat\theta_n^{(B)}\}$.
We consider five kinds of CIs.

\jy{can we give references to each of the method? How about the review paper in
  Statistical Science?}
\mc{references for percentile and BCA, couldn't find for centered, standard,
  or student's t}

@@

\paragraph{Bias Corrected and Accelerated ($BC_a$) Bootstrap CI}
The $BC_a$ CI was first suggested in \citet{efron1987better}.
\eds{a different abbrevation/notation was used for this in the introduction}
\mc{used $BC_a$}
\jy{Isn't this just the empirical CDF? We just need the sample quantile functon.
  What is your reference for this description?}
Let $\hat{z}_0 = \Phi^{-1}\{\#\{\hat\theta_n^{(b)} < \hat{\theta}_n\} / B\}$
for $b \in \{1, \ldots, B\}$. 
Let $Z_{(i)}$ be the original sample without the $i$th block $z_i$, and let
$\hat{\theta}_{n, -i}$ be the jackknife values of $Z_{(i)}$
for $i \in \{1, \ldots, n\}$, 
and let $a$ be $SKEW\{\hat{\theta}_{n, -i}\} / 6$. Then
$\hat\theta_{BC_a}[\alpha] = \hat{G}^{-1}\Phi(z_0 + \frac{z_{0} +
  z_{\alpha}}{1 - a(z_{0} + z_{\alpha})}).$
\eds{notation will need to be cleaned and clarified}
A $(1 - \alpha)$ centered $BC_a$ CI is
\[
(\hat\theta_{BC_a}[\alpha/2], \quad
\hat\theta_{BC_a}[1 - \alpha/2]).
\]
This CI is not necessarily centered by the point estimator $\hat\theta_n$. The
$BC_a$ method corrects for bias and skewness of the $B$ bootstrap point
estimates $\{\hat\theta_n^{(1)}, \ldots, \hat\theta_n^{(B)}\}$ by including
bias-correction and acceleration factors. The acceleration factor refers to
the 
rate of change of of the standard error of $\hat\theta_n$ with respect to
$\theta$.
\jy{why is it called BCA?}
\mc{addressed}

\paragraph{Standard Normal CI}

A $(1 - \alpha$ standard normal CI depends on the standard error $\hat{se}$
for each of the
$B$ bootstrap point estimates
$\{\hat\theta_n^{(1)}, \ldots, \hat\theta_n^{(B)}\}$. 
\[
(\hat{\theta}_{n} - z_{(1-\alpha/2)}*\hat{se}, \hat{\theta}_{n} -
z_{(\alpha/2)}*\hat{se}).
\]
This CI is centered by the point estimator $\hat\theta_n$ and is symmetric.
The standard
normal CI is a table-based bootstrap interval approach, which is to say that
it relies on the 
assumption that $\hat\theta_n$ is normally distributed and the expected value
of $\hat\theta_n$
is $\theta$.

\paragraph{Student's $t$ CI}
A $(1 - \alpha$ student's $t$ CI is
\[
(\hat{\theta}_{n} - t_{(1-\alpha/2), k - 1}*\hat{se}, \hat{\theta}_{n} -
t_{(\alpha/2), k -1}*\hat{se}),
\]
where k is the number of blocks.
This CI is centered by the point estimator $\hat\theta_n$ and is symmetric.
Like the standard 
normal interval, the student's t CI is a table-based bootstrap interval
approach. In this case,
we assume that $\hat\theta_n$ follows the $t_{k-1}$ distribution with an
expected value of $\theta$.

@@

Three target parameters of $X_t$ were considered:
1) $\mu = 0$, the mean of $X_t$;
2) $\sigma_x = 1$, the standard deviation of $X_t$; and
2) $\phi$, the lag-1 auto-correlation coefficient.
To investigate the effect of sample size~$n$, we considered an array of values
$n \in \{100, 200, 400, 800, 1600\}$. In each configuration, we generated 10000
replicates. For each replicate, we constructed three 95\% block bootstrap
CIs for each parameter as described in the last section. We can estimate 
$\mu$, $\sigma_x$, and $\phi$ by computing the sample mean, sample 
standard deviation,
and lag-1 auto-correlation, respectively, of each bootstrap sample, and then 
constructing intervals for each parameter using the appropriate procedures
described in Section~\ref{sec:bbci} .
Then we estimated their actual coverage rates along with their 95\% confidence
intervals from the 10000 replicates. The block bootstrap sampling step was done
with function \texttt{tsboot} from R package \textsl{boot} \citep{boot}, with
block size $\lceil n / l \rceil$. This function by default is an implementation
of moving block bootstrap as described in the previous section, meaning that
that blocks are allowed to wrap around, and $l = \lceil n^{1/3} \rceil$.
\jy{size? also it was overlapping blocks. Describe the details here.}
\mc{addressed}
\eds{Is $l = \lceil n^{1/3} \rceil$? Is it also worth investigating different 
choices of $l$ for fixed (large) $n$?}
\mc{Addressed in the Block Bootstrap Sample subsection}
\eds{how did you estimate $\mu$, $\sigma_x$ and $\phi$?}
\mc{addressed}

@@

\jy{Make it flow better and conciser}
The coverage rates of the CIs were used to compare the performance of CIs. Let
$\hat\theta_{L, r}$ and $\hat\theta_{U, r}$ be the lower and upper bound,
respectively, for the confidence interval constructed for each replicate
$r \in \{1, \ldots, R\}$, where $R$ is the
number of replicates.
Then $cov = \#\{\hat\theta_{L, r} < \theta < \hat\theta_{U, r} \}/R$,  
for $r \in \{1, \ldots, R\}$.
\eds{this notation is a bit sloppy, as it implies $n_{CI}$ changes for each 
value of $CI$; consider using a summation of indicators with a different index}
\mc{replaced $CI$ with $r$, and $n_{CI}$ with $R$}
If a CI method is valid, then the coverage rate is expected to match the
nominal 
level. Because it is unlikely for the coverage to exactly match the nominal
level,
we can construct a 95\% CI of the coverage
rate (which is an estimate of a proportion with $n = 10000$). If the proportion
0.95 is included in the interval, the block bootstrap method is likely
performing
well. If all values in the interval are below 0.95, the results would suggest 
that the
method either is providing inaccurate estimation, is underestimating the
process' variability, or a combination of both. If all values in the interval
are above .95, the results suggest that the method is overestimating the
process' variability.

If $\theta$ is not covered at that $n$, a larger $n$ may be
necessary, assuming that performance will improve as $n$ is increased.
Remember that
the goal of this study is to find the smallest $n$ which is sufficient for
proper coverage.

@@

\jy{One paragraph for each parameter; write down your observations in bullet
  points and then organize them into a logically flowing paragraph.}
\mc{paragraphs below}

Based on Figure~\ref{fig:mu}, 
the performance is about the same for Percentile, Centered, BCA, and 
Standard CIs with respect to estimating $\mu$. They more or less need
about the same sample size to have the correct coverage. For $\phi = -0.4$, 
they slightly over-cover $\mu$ for all sample sizes, but the error bars generally 
hover around the $95\%$ line. For $\phi = -0.2$, all four cover $\mu$ at the nominal 
rate when $n = 400$, and when $n = 1600$, although there seems to be a dip in 
coverage for $n = 800$. However, this deviation in trend can most likely be 
attributed to noise. Besides that, the coverage rates remain above $.9375$ 
for all sample sizes for this level of $\phi$. For $\phi = 0$, or when the 
sample is independently normally distributed, $n = 1600$ seems to 
be enough to recover $\mu$. For $\phi = 0.2$, the coverage rates are above 
$.9375$ when $n = 800$ and $n = 1600$, but the coverage intervals do not contain
$95\%$. Interestingly, there seems to be a drop in coverage rate from 
$n = 800$ to $n = 1600$. For $\phi = 0.4$, the coverage rates are above $.925$
when $n = 800$ and $n = 1600$, and there is a more noticeable downward 
trend from $n = 800$ to $n = 1600$. Student's $t$ CI has noticeably higher coverage
than the other CIs. For $\phi = -0.4$, the Student's $t$ CI actually 
over-covers $\mu$ for all sample sizes, and the lower error bars
are above the $95\%$ line for all sample sizes. For $\phi = -0.2$, it still slightly 
over-covers $\mu$ for all sample sizers, but the error bars generally hover
lower and around the $95\%$ line. For $\phi = 0$, the interval for the 
coverage rate contains $.95$ for all sample sizes. For $\phi = 0.2$ and 
$\phi = 0.4$, the trend in coverage is similar to the other CIs, but 
the overall coverage rates are higher, although they still do not reach the $95\%$
line.

Based on Figure~\ref{fig:sigma}, 
$BC_a$ CIs greatly undercover $\sigma_x$ for all sample sizes, although
there is no trend of coverage deterioration, indicating that there may eventually
a sample size large enough for $\sigma_x$ to be covered at the nominal level.
However, because it's performance is so much poorer than the other CIs,
$BC_a$ should not be used. Percentile, Centered, and Standard CIs perform similarly,
with respect to estimating $\sigma_x$. For $\phi = -0.4$, $\phi = -0.2$, and $\phi = 0$, 
$n = 1600$ seems to be large enough to cover $\sigma_x$ at the nominal level
when using the Standard Normal CI interval, while the others are very close, hovering
around $.945$ for $n = 1600$. For $\phi > 0$, a larger sample size does seem
to be necessary to cover $\sigma_x$ at the nominal rate. However, for $\phi = 0.2$, 
when $n \geq 400$, coverage is above $.93$ for all three of these CIs. For $\phi = 0.4$,
when $n = 1600$, coverage is above $.93$ for all three of these CIs.
Like for $\mu$, Student's $t$ CIs have the highest overall coverage of $\sigma_x$.
Additionally, the Student's $t$ method does not over-cover $\sigma_x$ for any $n$.
For $\phi = -0.4$, $\sigma_x$ is covered at the nominal rate for $n \geq 1600$.
For $\phi = -0.2$ and $\phi = 0$, $\sigma_x$ is covered at the nominal rate for $n \geq 400$.
For $\phi = 0.2$, although the coverage does not reach the $95\%$ line by $n = 1600$, 
it seems to be around $.945$ for $n \geq 400$
For $\phi = 0.4$, although the coverage does not reach the $95\%$ line by $n = 1600$, 
it seems to be above $.93$ for $n \geq 400$

Based on Figure~\ref{fig:phi}, 
Percentile and $BC_a$ CIs deteriorate clearly for any level of temporal correlation,
so they should not be used. The deterioration becomes more evident
as the absolute value of $\phi$ increases, regardless of whether $\phi$ is 
negative or positive. Centered and Standard CIs perform similarly;
a sample size of $n = 800$ appears to be sufficient to recover $\phi$ at the 
nominal level when using either of these two CIs. 
Student's $t$ CIs appear to recover $\phi$ at the nominal level for $n \geq 100$ for all 
$\phi$.
\jy{One summary paragraph at the end.}
\mc{paragraph below}

To summarize, the CI type chosen should be based on the target parameter. 
When estimating $\mu$, the Student's t CI seems to have the highest coverage
overall, although that leads to over-coverage when $\phi$ is -0.4. For a
sample with no temporal dependence, the Student's t CI cover $\mu$ perfectly
at the nominal rate even for small sample sizes. For positive $\phi$, a larger
sample size appears to be necessary regardless of the CI used. In the case
that $\phi$ is unknown and expected to be greater than $0$, $n > 1600$ may be
necessary for block bootstrap interval estimation of $\mu$. If that is not the
case, a lesser sample size is likely sufficient. When estimating $\sigma$,
$BC_a$ should not be used, and Student's t again has the greatest coverage
rates. In the case that $\phi$ is unknown and expected to be greater than $0$,
$n > 1600$ may be necessary for block bootstrap interval estimation of
$\sigma$. If that is not the case, a lesser sample size is likely sufficent.
When estimating $\phi$, Percentile and $BC_a$ CIs 
deteriorate in coverage, indicating they should not be used in this context. 
Increasing n will not fix the performance of either of these intervals 
because the assumption that the coverage rate will approach the nominal level
as n increases is invalid. Centered and Standard CIs managed to fix the
deterioration problem, and they perform similarly, but Student's t covers
$\phi$ at the nominal rate for small sample sizes regardless of the absolute
value or sign of $\phi$. Interestingly, $n = 100$ seems to be large enough to
recover $\phi$ when using the Student's t method.

@@

When using $\hat{\theta}_{n}$-centered intervals and $\phi$ is
unknown, the results of this study suggest that an $n$ of around $1600$ may be
necessary for common practice to estimate a simple parameters like $\mu$ 
or $\sigma_x$. If $\phi$ is already known, a lesser $n$ may be adequate
to
estimate these parameters. ... However, in real world applications, $\phi$ is
more commonly found to be positive, so a larger $n$ is more likely to be
necessary. Lastly, to estimate $\phi$, an $n$ of around $100$ using the Student's $t$ method
 may be sufficient
Further investigation may be necessary to see if there are other interval
corrections that fix the coverage deterioration problem for $\phi$.
